%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
        {Front-end developer (intern)} % Job title
        {Daowen Network Technology} % Organization
        {Hangzhou, China} % Location
        {May. 2017 - Aug. 2017} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item Related Skills: JavaScript, HTML5/CSS3, less, JQuery, Bootstrap3, webpack2, ejs, git.
                \item Designed and implemented the architecture of a portal website.
                \item The webpack2 was used as a module bundler to build the multi-page website. 
                \item Bootstrap3 was used as a UI library to support responsive design.
                \item Jquery was used to build elements which need to interact with user and database.
                \item Git was used as a version control tool in the team.
                \item {\href{http://www.chenggua.com/}{Chenggua Portal Website: http://www.chenggua.com/.}}
            \end{cvitems}
        }

%---------------------------------------------------------
    \cventry
        {Front-end developer (intern)} % Job title
        {Zhejiang Equity Exchange} % Organization
        {Hangzhou, China} % Location
        {May. 2014 - Aug. 2014} % Date(s)
        {
            \begin{cvitems} % Description(s) of tasks/responsibilities
                \item Related Skills: JavaScript, HTML/CSS, JQuery.
                \item Testing and maintenance the company's website.
                \item Based on the company's website, optimized the user interface using HTML/CSS.
                \item Launched several website pages made by HTML, CSS and JQuery.
                \item The website is too old and has been replaced.
            \end{cvitems}
        }

%---------------------------------------------------------
\end{cventries}


